Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

\extraspacing {\bf Math Conventions.} For any integer $x \ge 1$, we use $[x]$ to represent the set $\set{1, 2, ..., x}$. Every mention of the word ``rectangle'' henceforth will refer to an axis-parallel rectangle. \todo{more?}

@@

SJs have been extensively studied in the database-system community, leading to the development of numerous methods that, although lacking strong theoretical guarantees, demonstrate excellent empirical performance in real-world applications. We refer interested readers to \cite{apr+00,mp01,???} as entry points into the literature.

@@

From the perspective of theory, SJs are best understood when $k = 2$, i.e., the {\em pairwise} scenario, where it is folklore that the problem can be solved in $O(n \log n + \out)$ time using $O(n)$ space (see, e.g., \cite{bcko08}). However, the problem becomes significantly more challenging for $k \ge 3$, i.e., the {\em multiway} scenario. All the solutions developed (see \cite{mp98,mp01,pmt99,???} and the references therein) before 2022 suffer from a worst-case time complexity of $O(n^k)$, offering essentially no improvement over the naive method that simply enumerates the entire cartesian product $R_1 \times R_2 \times ... \times R_k$.

>>>>

\extraspacing {\bf Math Conventions.} For any integer $x \ge 1$, we use $[x]$ to represent the set $\set{1, 2, ..., x}$. Every mention of the word ``rectangle'' henceforth will refer to an axis-parallel rectangle. Every logarithm has base 2 by default.

@@

SJs have been extensively studied in the database-system community, leading to the development of numerous methods that, although lacking strong theoretical guarantees, demonstrate excellent empirical performance in real-world applications. We refer interested readers to \cite{apr+00,bks93,gcn+13,js07,ks97,lr94,lr96,mp98,mp01,mp03,pd96,pmt99} as entry points into the literature.

@@

From the perspective of theory, SJs are best understood when $k = 2$, i.e., the {\em pairwise} scenario, where it is folklore that the problem can be solved in $O(n \log n + \out)$ time using $O(n)$ space (see, e.g., \cite{bcko08}). However, the problem becomes significantly more challenging for $k \ge 3$, i.e., the {\em multiway} scenario. All the solutions developed (see \cite{gcn+13,mp98,mp01,pmt99} and the references therein) before 2022 suffer from a worst-case time complexity of $O(n^k)$, offering essentially no improvement over the naive method that simply enumerates the entire cartesian product $R_1 \times R_2 \times ... \times R_k$.
